How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-27 docs/PhysicsPaper/StokesErosion.tex
NM

As discussed in Section \ref{subsec:anis}, the anisotropy of the medium results from the combination of {\em shape} anisotropy, at the individual grain level, and {\em configurational anisotropy}, at the large-scale level. As detailed in Section \ref{subsec:anis}, the configurational anisotropy can be extracted by replacing any collection of partially-eroded bodies with circles having the same areas and centers of mass and measuring the anisotropy of the resulting configuration. We perform this process at every time step in the simulation, and show in Fig.~\ref{fig3}(a) both permeabilities, $k_{11}^{(c)}$ and $k_{22}^{(c)}$, of the corresponding circle configurations. As seen in the figure, the permeabilities of the circle configurations always lie in between the true values $k_{11}$ and $k_{22}$ of the eroded geometries.

%Text for Fig 3: 
%The anisotropy of permeability grows large, up to a value of 4 during the middle portion of the simulation. The figure also shows the anisotropy of the circular grid.

>>>>

As discussed in Section \ref{subsec:anis}, the anisotropy of the medium results from the combination of {\em shape} anisotropy, at the individual grain level, and {\em configurational anisotropy}, at the large scale. As detailed in Section \ref{subsec:anis}, the configurational anisotropy can be extracted through a process in which, at any point in time, the configuration of partially-eroded bodies is replaced with a collection of circles having the same areas and centers of mass. We perform this process and show in Fig.~\ref{fig3}(a) the permeabilities, $k_{11}^{(c)}$ and $k_{22}^{(c)}$, of the corresponding circle configurations. As seen in the figure, the permeabilities of the circle configurations always lie in between the values, $k_{11}$ and $k_{22}$, of the true, eroded medium. The {\em configurational} anisotropy is then computed as the permeability ratio of the circle configuration, $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$, and then the {\em shape} anisotropy can be determined through $\anis_S = \anis/\anis_C$. As seen in Fig.~\ref{fig3}(b), the shape anisotropy is the larger factor throughout the majority of the simulation, implying that the shape of individual grains plays a larger role than their relative positions. It is only during the last 10\% of the simulation that the configurational anisotropy grows significantly and surpasses the shape anisotropy. This relative growth of the configurational anisotropy corresponds to the strong channelization seen in the last panel of Fig.~\ref{fig1}.

The late emergence of substantial configurational anisotropy may seem like a spurious effect that is particular to the one simulation shown in Fig.~\ref{fig3}. However, statistical analysis of many simulations will show this feature to emerge robustly in simulations with a relatively large number of bodies $M \ge 60$.
